---
title: "R Notebook"
output: html_notebook
---

libraries 

```{r}
# install.packages('smotefamily')
library(smotefamily)
library(magrittr)
library(data.table)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
data_example = data.table(sample_generator(10000,ratio = 0.80))
data_example
```
```{r}
data_example[, .N, by=result][order(result)]
```

```{r}
genData = SMOTE(data_example[,.(X1, X2)],data_example[,result])
genData
```
```{r}
data_example_mod <- data.table(genData$data)
data_example_mod
```
```{r}
data_example_mod[, .N, by=class][order(class)]
```
```{r}
genData_2 = SMOTE(data_example[,.(X1, X2)],data_example[,result],K=7)
genData_2
```
```{r}
data_example_mod_2 <- data.table(genData_2$data)
data_example_mod_2
```
```{r}
data_example_mod_2[, .N, by=class][order(class)]
```

